### 2014-06-22 dicook/possessions.Rmd
looking at possessions, age

```{r plotstuff, fig.width=8, fig.height=8, warning=FALSE, message=FALSE}
qplot(numposs, PV1MATH, data=student2012.sub, alpha=I(0.1), geom=c("point", "smooth"))
qplot(numedposs, PV1MATH, data=student2012.sub, alpha=I(0.1), geom=c("point", "smooth"))
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub$PV1MACC <- as.numeric(student2012.sub$PV1MACC)
student2012.sub$PV1MACQ <- as.numeric(student2012.sub$PV1MACQ)
student2012.sub$PV1MACS <- as.numeric(student2012.sub$PV1MACS)
student2012.sub$PV1MACU <- as.numeric(student2012.sub$PV1MACU)
student2012.sub$PV1MAPE <- as.numeric(student2012.sub$PV1MAPE)
student2012.sub$PV1MAPF <- as.numeric(student2012.sub$PV1MAPF)
student2012.sub$PV1MAPI <- as.numeric(studen=t2012.sub$PV1MAPI)
student2012.sub$PV1READ <- as.numeric(student2012.sub$PV1READ)
student2012.sub$PV1SCIE <- as.numeric(student2012.sub$PV1SCIE)
student2012.sub.summary <- summarise(group_by(student2012.sub[,c(1,8:39)], name), math=mean(PV1MATH, na.rm=T), 
          read=mean(PV1READ, na.rm=T), science=mean(PV1SCIE, na.rm=T),
          poss = mean(numposs, na.rm=T), edposs = mean(numedposs, na.rm=T))
qplot(poss, math, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
qplot(poss, read, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
qplot(poss, science, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
head(student2012.sub.summary[order(student2012.sub.summary$math, decreasing=T),], 20) 
# Vietnam is the outlier, few poss, high scores
lm(math~poss, data=student2012.sub.summary)
# Each increase in one possession tends to increase math score by 25 points (poss=7, 12)
qplot(edposs, math, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
qplot(edposs, read, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
qplot(edposs, science, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
lm(math~edposs, data=student2012.sub.summary)
# Each increase in one possession tends to increase math score by 13 points (edposs=5, 14)
qplot(edposs, poss, data=student2012.sub.summary)
```

>>>>

```{r plotstuff, fig.width=8, fig.height=8, warning=FALSE, message=FALSE}
qplot(numposs, PV1MATH, data=student2012.sub, alpha=I(0.1), geom=c("point", "smooth"))
qplot(numedposs, PV1MATH, data=student2012.sub, alpha=I(0.1), geom=c("point", "smooth"))
student2012.sub$PV1MATH <- as.numeric(student2012.sub$PV1MATH)
student2012.sub$PV1MACC <- as.numeric(student2012.sub$PV1MACC)
student2012.sub$PV1MACQ <- as.numeric(student2012.sub$PV1MACQ)
student2012.sub$PV1MACS <- as.numeric(student2012.sub$PV1MACS)
student2012.sub$PV1MACU <- as.numeric(student2012.sub$PV1MACU)
student2012.sub$PV1MAPE <- as.numeric(student2012.sub$PV1MAPE)
student2012.sub$PV1MAPF <- as.numeric(student2012.sub$PV1MAPF)
student2012.sub$PV1MAPI <- as.numeric(student2012.sub$PV1MAPI)
student2012.sub$PV1READ <- as.numeric(student2012.sub$PV1READ)
student2012.sub$PV1SCIE <- as.numeric(student2012.sub$PV1SCIE)
student2012.sub.summary <- summarise(group_by(student2012.sub[,c(1,8:39)], name), math=mean(PV1MATH, na.rm=T), 
          read=mean(PV1READ, na.rm=T), science=mean(PV1SCIE, na.rm=T),
          poss = mean(numposs, na.rm=T), edposs = mean(numedposs, na.rm=T))
qplot(poss, math, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
qplot(poss, read, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
qplot(poss, science, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
head(student2012.sub.summary[order(student2012.sub.summary$math, decreasing=T),], 20) 
# Vietnam is the outlier, few poss, high scores
lm(math~poss, data=student2012.sub.summary)
# Each increase in one possession tends to increase math score by 25 points (poss=7, 12)
qplot(edposs, math, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
qplot(edposs, read, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
qplot(edposs, science, data=student2012.sub.summary) + geom_smooth(method="lm", se=F)
lm(math~edposs, data=student2012.sub.summary)
# Each increase in one possession tends to increase math score by 13 points (edposs=5, 14)
qplot(edposs, poss, data=student2012.sub.summary)
```
